Manuscript drafts

### 2020-02-25 manuscript/drafts/manuscript.Rmd
knit
update notes, add manuscript texts on data, update references

---
title: "Manuscxript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(knitr)
library(xtable)
library(kableExtra)
# load model parameters 
source("asr-parameters.R")
```

@@

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
``` 
# Analysis strategy
Goal: evaluate performance of different models of the ASReview tool.

@@

```{r}
kable(tab, "latex", booktabs = TRUE, col.names = "Configurations") %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(2, width = "30em") 
```

@@

## Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets.

### Datasets

#### ptsd
#### ace
#### hall 
#### nagtegaal - van PhD van Lars
#### medische van Jan

@@

tabbie <- tabbie[c(1,3,5,6,9),]
row.names(tabbie) <- NULL
tabbie %>%
  kable(col.names = names(words)[1:3], format = "latex")
```

@@

- 1 on 1: maximum performance 
- 4 on 1: cross-validation 
- 5 on 1: more data = more better?

@@

@@

#### Work saved over sampling (WSS)
Indicates how much time can be saved, at a given level of recall.
WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
Typically, WSS is measured at a recall of 0.95.

$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall ) $$

@@

>>>>

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(knitr)
library(xtable)
library(kableExtra)
library(captioner)
library(glue)

# load model parameters 
source("asr-parameters.R")

# path to all R folder
pathRdata <- "../../R/data/"
```

@@

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
```

```{r all tables, results = 'hide'}
table_nums <- captioner(prefix = "Table")
table_nums(name = "datasets", caption = "Descriptive statistics on articles and resulting datasets for each original systematic review.")
```

# Introduction
SR are booming
ML tools as well

[@PRISMA-PGroup2015]

What must be the objective of our tool?

Selecting papers is a two-step process: abstract & fulltext screening

# Methods
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
annotated include/exclude

## Datasets
The data consists of five open datasets on systematic reviews from various research areas. 
All datasets are openly available.
The raw files were preprocessed. Duplicate entries were removed.
Entries with missing abstracts were removed. 
Preprocessing scripts can be found on the GitHub repository

Descriptive statistics on the five systematic reviews can be found in Table `r table_nums("datasets", display = "cite")`.

```{r}
# datasets table
load(paste0(pathRdata, "datasets_table.Rdata"))

tibble(Dataset = names(all), 
       #Citation = NA, # maybe add footnote citation with kableExtra i.o. this.
       `No. studies` = sapply(all, function(x) x[1,1]), 
       `No. selected for fulltext screening` = sapply(all, function(x) x[1,2]),
       `No. final inclusions` = sapply(all, function(x) x[1,3]),
       `Inclusion rate (%)` = sapply(all, function(x) round(x[1,3]/x[1,1]*100,2)),
       `No. studies in test collection` = sapply(all, function(x) x[3,1]),
       `No. selected for fulltext screening test collection` = sapply(all, function(x) x[3,2]),
       `No. final inclusions in test collection` = sapply(all, function(x) x[3,3]),
       `Inclusion rate in test collection (%)` = sapply(all, function(x) round(x[3,3]/x[3,1]*100,2))
       ) %>%
  # knitr kable
  kable(format = "latex",
        booktabs = TRUE,
        caption = table_nums("datasets")) %>%
  kable_styling(full_width = TRUE) %>%
  add_header_above(c("", "Original study" = 4, "Test collection" = 4))

  # add citations
```

The inclusion rate is ... data is imbalanced. 
what is the philosophy
False negatives must be avoided ... 
The cost of a false negative outweighs the cost of a false positive. 
Note that we assume the oracle/original user to hold the truth. 
This is of course not always the case.

## Models 
Five different models were applied on the data.

### Optimizing Hyperparameters 
Every model has its own hyperparameters. 
For every model, the hyperparameters are optimized three times, arriving at three versions of the model:

@@

```{r}
tab %>%
kable(format = "latex", 
      booktabs = TRUE, 
      col.names = "Configurations") %>%
  kable_styling(full_width = TRUE)
```

@@

### Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets.

#### ACE
The ACEInhibitors dataset from the study by [@Cohen2006]. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.

WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
The data

#### ptsd
The review  
The data

#### hall 
The review [@Hall2012], is reviewed in [@Yu2016].

#### nudging
The review [@Nagtegaal2019]
The data [@Nagtegaal2019a]

Paper says: 
- systematic search n = 2006
- full text screening n = 377
- included in synthesis n = 100

Open data online says:

- systematic search n = 
- full text screening n = 
- included in synthesis n = 101 (18?)

abstract excel sheet private says: 
- systematic search n = 2018
- full text screening n = 
- included in synthesis n = 118

Difference in 18 inclusions = systematic reviews. to exclude/include?

#### Wilson
The review [@Appenzeller-Herzog2019]
The dataset [@Appenzeller-Herzog2020]

- systematic search n = 3453
- full text screening n = 174
- included in synthesis n = 26

@@

tabbie <- tabbie[c(1,3,5,6,9),]
row.names(tabbie) <- NULL

tabbie %>%
  kable(col.names = names(words)[c(1,3)], 
        format = "latex",
        booktabs = TRUE)
```

@@

- 1 on 1: maximum performance

$$ d = D $$
- 4 on 1: cross-validation 
$$ d \notin D$$

$$ D = {1, 2, 3, 4}$$

- 5 on 1: more data = more better?

$$ d \in D $$

@@

## Evaluation

@@

#### Work saved over sampling (WSS)
Indicates how much time can be saved, at a given level of recall.
WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
Typically, WSS is measured at a recall of 0.95. Reasonable because..

$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$

@@

Is performance related to some characteristic (n, inclusion rate, ...)

## Cross-validation
Should give an accurate estimate of maximum performance / future systematic reviews to be performed.
